Measuring the Utility of a Collision:\\ The Neighborhood of MD4 Collisions

### 2017-11-27 dsn-2018/bare_conf.tex
Outline remaining portion of paper
Signed-off-by: Alexander Scheel <alexander.m.scheel@gmail.com>

% *** MATH PACKAGES ***
%
%\usepackage{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
%
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

@@

@@

\section{Conclusion}
The conclusion goes here.

@@

The authors would like to thank the Department of Electrical and Computer
Engineering.

>>>>

% *** MATH PACKAGES ***
%
\usepackage{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
%
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath

% *** SPECIALIZED LIST PACKAGES ***
%
\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

@@

\section{Techniques for Logical Cryptanalysis}

The following techniques have been extensively tested on MD4 and partially
tested on MD5 and believe to apply fully to MD5. They may or may not apply
to any later hash function, such as SHA-1, SHA-2, or SHA-3, and have not been
tested yet.

In the following sections, we use the collisions of X. Wang \cite{Wang2005},
Y. Sasaki \cite{Sasaki2007}, M. Schlaffer \cite{Schlaffer2006}, H. Dobbertin
\cite{Dobbertin1998}, and P. Kasselman \cite{KasselmanMD4} for examples.

\subsection{Distance Metric}

We introduce a distance function between collision classes by the number of
differences in intermediate rounds deltas. We find justification for this
metric in the existing literature on MD4: H. Dobbertin's \cite{Dobbertin1998}
and P. Kasselman's \cite{KasselmanMD4} classes have distance $1$ under this
metric.

That is:
\begin{align}
    \delta(C_1, C_2) = \| \{ i : I(C_1, i) \neq I(C_2, i) \} \|
\end{align}

For the example collisions, below are distances under this metric:
\textbf{TODO}.

\subsection{Neighborhood}

We define the neighborhood of a collision class to be all other collisions
which have a distance of one.

That is:
\begin{align}
    N(C) = \{ C_j : \delta(C, C_j) = 1 \}
\end{align}

For the example collisions, below are sizes of the neighborhoods:
\textbf{TODO}.

\subsection{Reduced Rounds}
\subsubsection{Abstract}

\textbf{TODO} - Describe technique applied to tags

Give some reasoning for why it works, example graphs.

\subsubsection{Neighborhood}

\textbf{TODO} - Describe technique applied neighborhood extensions

Give some reasoning for why it works, example graphs.

\section{Empirical Results}
\subsection{Unique Differentials}

\textbf{TODO}

Include graphic of count of unique differentials for all 35k collision classes

Separate table for known attacks as data points. Examples in appendix?

\subsection{Unit-Step Neighborhood}

\textbf{TODO}

Include graphic of count of number of neighbors for all 35k collision classes

Separate table for known attacks as data points.

\subsection{Zeroes \& Ones}

\textbf{TODO}

Include graphic of count of max number of zeros/ones for all 35k collision
classes.

Separate table for known attacks as data points. Examples as appendix.

\subsection{Multicollisions}

\textbf{TODO}

Include table detailing how many have multicollisions and how many don't.
Hypothesis: all do since all existing datapoints do.

Separate table for known attacks as data points. Examples as appendix.

\subsection{ASCII Blocks}

\textbf{TODO}

Include table detailing how many have ASCII blocks and how many don't.

Separate table for known attacks as data points. Examples as appendix.

\section{Open Research}

The framework can be seen here \textbf{TODO}. Complete data set available
upon request.

@@

\section{Conclusion}

The conclusion goes here.

@@

The authors would like to thank the Department of Electrical and Computer
Engineering and Nathan Mulbrook for providing hardware.
